Unified Convergence Analysis of FedAve on Non-IID Data

### 2020-05-26 source/sec_exp.tex
update figures

% where we generated i.i.d. data $\vx_i^k$ for all devices. At each communication round, all devices participated
% in synchronization. 
\textbf{Linear speedup.} To verify the linear speedup results in theorems {\color{red}add theorem id}, we evaluate the number of iterations needed to reach
$\epsilon$-accuracy in three objectives. We initialize all runs with $w_0 = \textbf{0}_d$ and measure. For each configuration, we run three random seeds and report
the best seed results for each configuration $(E, K)$. In each configure, we
extensive search the stepsize from $\min(\eta_0, \frac{nc}{1 + t})$, where
$\eta_0 \in \{0.1, 0.12, 1, 32 \}$ according to different problems and $c$ can
take the values $c = 2^u \forall i \in \ZZ$. For the detailed experimental setup,
please refer to the appendix. As the results shown in Figure~\ref{fig:speedup},
the number of iterations to reach the target accuracy $\epsilon$ decreasing 
as the number of workers increase.

>>>>

% where we generated i.i.d. data $\vx_i^k$ for all devices. At each communication round, all devices participated
% in synchronization. 
\textbf{Linear speedup.} To verify the linear speedup results in Theorem~\ref{th:strongcvxsmth}~\ref{th:cvxsmoth}~\ref{th:fedmasslr}, we evaluate the number of iterations needed to reach
$\epsilon$-accuracy in three objectives. We initialize all runs with $w_0 = \textbf{0}_d$ and measure. For each configuration, we run three random seeds and report
the best seed results for each configuration $(E, K)$. In each configure, we
extensive search the stepsize from $\min(\eta_0, \frac{nc}{1 + t})$, where
$\eta_0 \in \{0.1, 0.12, 1, 32 \}$ according to different problems and $c$ can
take the values $c = 2^u \forall i \in \ZZ$. For the detailed experimental setup,
please refer to the appendix. As the results shown in Figure~\ref{fig:speedup},
the number of iterations to reach the target accuracy $\epsilon$ decreasing 
as the number of workers increase.
